Online reprocessing simulation for thorium-fueled molten salt breeder reactor

### 2017-07-07 msbr_reproc.tex
consist->consisting

\begin{document}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}
The thermal spectrum \gls{MSR} is an advanced type of reactor consist of constantly circulating liquid fuel (i.e., mixture of $LiF-BeF_2-ThF_4-UF_4$ or $LiF-BeF_2-ZrF_4-UF_4$) which works also as a coolant, and the reactor graphite as moderator. This fuel form leads to immediate advantages over traditional, solid-fueled, reactors. The molten-salt carrier salt with dissolved in it fissile and/or fertile material allows to use online refuelling and reprocessing, which means \gls{MSR}s can operate years without shutdown, achieve maximum fuel utilization, and outstanding neutron economy \cite{leblanc_molten_2010}. Moreover, this type of fuel does not need fabrication and could be transported from enrichment plant to \gls{NPP} in form of uranium hexafluoride ($UF_6$), so \gls{MSR}s are also beneficial with regards to economics. Additionally, it has high level of inherent safety due to strong negative temeperature coefficient of reactivity, near-atmospheric pressure in the primary loop, stable coolant, passive decay heat cooling, and small excess reactivity \cite{elsheikh_safety_2013}.

>>>>

\begin{document}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}
The thermal spectrum \gls{MSR} is an advanced type of reactor consisting of constantly circulating liquid fuel (i.e., mixture of $LiF-BeF_2-ThF_4-UF_4$ or $LiF-BeF_2-ZrF_4-UF_4$) which works also as a coolant, and the reactor graphite as moderator. This fuel form leads to immediate advantages over traditional, solid-fueled, reactors. The molten-salt carrier salt with dissolved in it fissile and/or fertile material allows to use online refuelling and reprocessing, which means \gls{MSR}s can operate years without shutdown, achieve maximum fuel utilization, and outstanding neutron economy \cite{leblanc_molten_2010}. Moreover, this type of fuel does not need fabrication and could be transported from enrichment plant to \gls{NPP} in form of uranium hexafluoride ($UF_6$), so \gls{MSR}s are also beneficial with regards to economics. Additionally, it has high level of inherent safety due to strong negative temeperature coefficient of reactivity, near-atmospheric pressure in the primary loop, stable coolant, passive decay heat cooling, and small excess reactivity \cite{elsheikh_safety_2013}.
